\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex

The likely prevalence of continents, oceans, and complex weather patterns 
on Sol d make it an extremely promising site for the evolution of life. 
We strongly advocate for future missions to further investigate this possibility. 
In particular, Sol d may be a good choice of target for a lander mission. 
One prime landing site is located at the planetary (latitude, longitude) coordinates 
(\href{https://www.google.com/maps/place/Roswell,+NM/@36.2909732,-94.0798131,3.96z/data=!4m5!3m4!1s0x86e2651365aced55:0xe41b0be474cfd77e!8m2!3d33.3942655!4d-104.5230242}{$33.3943^\circ$ N, $104.5230^\circ$ W}).%
\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (private communication, Andrew R. Casey) led us to conclude that this would not be a suitable location.}

The work presented here also serves as a relevant case study for future 
efforts to characterize terrestrial exoplanets. \todo{(more)}

>>>>

The likely prevalence of continents, oceans, and complex weather patterns 
on Sol d make it an extremely promising site for the evolution of life. 
We strongly advocate for future missions to further investigate this possibility. 
In particular, Sol d may be a good choice of target for a lander mission. 
One prime landing site is located at the planetary (latitude, longitude) coordinates 
(\href{https://www.google.com/maps/place/Roswell,+NM/@36.2909732,-94.0798131,3.96z/data=!4m5!3m4!1s0x86e2651365aced55:0xe41b0be474cfd77e!8m2!3d33.3942655!4d-104.5230242}{$33.3943^\circ$ N, $104.5230^\circ$ W}).%
\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (Andrew R. Casey, personal communication) led us to conclude that this would not be a suitable location.}

The work presented here also serves as a relevant case study for future 
efforts to characterize terrestrial exoplanets. While the circumstances of \TESS's 
observations of Sol d will not be replicated exactly for other planets, similar 
rotationally-modulated phase curves of reflected light may be feasible in the future. 
We show that a fast, analytic linear model can be successfully applied to such data. 
We also underscore the importance of high cadence \emph{and} long duration for 
these observations, and we advocate for multi-wavelength coverage to 
help disentangle the photometric signatures of continents and persistent cloud features.
